Enforced Invariant Confluence

### 2016-11-26 doc/counters.tex
Removed todone todos.
Tidied up implication figure.
Added 0-isafety/istrength proofs.

\subsection{\iconfluence{} Alternatives}
\begin{itemize}
  \item \todo{\istrengthstar $\centernot \implies$ \iconfluence?}
  \item \todo{\iconfluence $\implies$ \istrengthstar?}
  \item \todo{\istrength $\centernot \implies$ \isafety?}
  \item \todo{\isafety $\implies$ \istrength?}
  \item \todo{\istrength $\centernot \implies$ \iconfluence?}
  \item \todo{\iconfluence $\implies$ \istrength?}
  \item \todo{Find something between \isafety{} and \iconfluence.}
  \item \todo{1-iconfluence with derived txns to start}
\end{itemize}

@@

@@

  \begin{tikzpicture}
    \node[] (0-isafety) at (0, 0) {0-\isafety};
    \node[] (1-isafety) at (0, -2) {1-\isafety};
    \node[] (k-isafety) at (0, -4) {$k$-\isafety};
    \node[] (istrengthstar) at (6, 0) {\istrengthstar};
    \node[] (ipreservation) at ($(0-isafety) + (30:3)$) {\ipreservation};
    \node[] (iconfluence) at ($(0-isafety) + (-30:3)$) {\iconfluence};
    \node[] (k-iconfluence) at ($(iconfluence) + (4, 0)$) {$k$-\iconfluence};
    \node[] (1-iconfluence) at ($(k-iconfluence) + (4, 0)$) {1-\iconfluence};

    \draw[impl] (0-isafety) -> (ipreservation);
    \draw[impl] (0-isafety) -> (iconfluence);
    \draw[impl] (iconfluence) -> (k-iconfluence);
    \draw[impl] (k-iconfluence) -> (1-iconfluence);
    \draw[impl] (0-isafety) -> (istrengthstar);
    \draw[impl] (istrengthstar) -> (iconfluence);
    \draw[impl] (istrengthstar) -> (ipreservation);
    \draw[impl] (0-isafety) -> (1-isafety);
    \draw[impl] (1-isafety) -> (k-isafety);
  \end{tikzpicture}

>>>>

\subsection{\iconfluence{} Alternatives}
\begin{itemize}
  \item \todo{\istrength $\centernot \implies$ \isafety?}
  \item \todo{\isafety $\implies$ \istrength?}
  \item \todo{\istrength $\centernot \implies$ \iconfluence?}
  \item \todo{\iconfluence $\implies$ \istrength?}
  \item \todo{\istrengthstar $\implies$ \istrength?}
  \item \todo{\istrength $\implies$ \istrengthstar?}
  \item \todo{Find something between \isafety{} and \iconfluence.}
  \item \todo{1-iconfluence with derived txns to start}
\end{itemize}

@@

\begin{claim}\label{clm:0-isafety-implies-istrength}
  0-\isafety{} $\implies$ \istrength{}.
\end{claim}
\begin{proof}
  Consider an arbitrary set of \imp{} transactions $T$ that is 0-\isafe{} with
  respect to invariant $I$; we show $T$ is \istrong{} with respect to $I$. Let
  $G_0 = I \times I$. $T2$ holds trivially. For all $c \in T$, let $n = 1$ and
  $P_n = Q_n = I$. T3b, T3c, and T3d reduce to $I \subseteq I$, $I \subseteq
  I$, and $G_0(I) \subseteq I$ which all hold trivially. T3e reduces to $I
  \times \denote{c}(I)(I) \subseteq G_0$. To prove this, it is sufficient to
  prove $\denote{c}(I)(I) \subseteq I$ which holds directly from 0-\isafety{}.
\end{proof}

\begin{claim}\label{clm:0-istrength-not-implies-0-isafety}
  \istrength{} $\centernot\implies$ 0-\isafety.
\end{claim}
\begin{proof}
  Consider a database over a single variable $x$. For convenience, we'll denote
  database states as integers. Let
  \begin{itemize}
    \item
      $G_0 \defeq \set{(0, 0)} \cup \setst{(a, b)}{a \geq 2, b \geq 2}$;
    \item
      $I \defeq x = 0 \lor x \geq 2$;
    \item
      the single \imp{} transaction $c \defeq
      \impif{read(x)=0}{add(x, 0)}{add(x, 1)}$;
    \item
      $n \defeq 2$;
    \item
      $P_1 \defeq Q_1 \defeq \set{0}$; and
    \item
      $P_2 \defeq Q_2 \defeq \setst{x}{x \geq 2}$.
  \end{itemize}

 First note that $c$ is \istrong{} with respect to $I$.  T2, T3b, T3c, and T3d
 hold trivially. For $i = 1$, T3e reduces to $\set{0} \times
 \denote{c}(\set{0})(\set{0}) \subseteq G_0$ which holds because $\set{(0, 0
 \circ \denote{c}(0)} = \set{(0, 0)} \subseteq G_0$. For $i = 2$, consider
 arbitrary databse states $x,y,z \in P_2 = G_2$. $(x, y \circ \denote{c}(z)) =
 (x, y + 1) \in G_0$. Thus T3e holds for $i = 2$.

  Now note that $c$ is not 0-\isafe{} with respect to $I$. Notably, $I(0)$ and
  $I(2)$, but $0 \circ \denote{c}(2) = 0 + 1 = 1$ does not satisfy $I$.
\end{proof}

@@

  \begin{tikzpicture}
    \node[] (0-isafety) at (0, 0) {0-\isafety};
    \node[below=of 0-isafety]     (1-isafety)     {1-\isafety};
    \node[below=of 1-isafety]     (k-isafety)     {$k$-\isafety};
    \node[right=of 0-isafety]     (istrengthstar) {\istrengthstar};
    \node[above=of istrengthstar] (ipreservation) {\ipreservation};
    \node[right=of istrengthstar] (iconfluence)   {\iconfluence};
    \node[below=of iconfluence]   (k-iconfluence) {$k$-\iconfluence};
    \node[below=of k-iconfluence] (1-iconfluence) {1-\iconfluence};
    \node[below=of istrengthstar] (istrength)     {\istrength};

    \draw[ultra thick, impl] (0-isafety) -> (istrengthstar);
    \draw[ultra thick, impl] (istrengthstar) -> (iconfluence);
    \draw[ultra thick, impl] (0-isafety) -> (istrength);
    \draw[impl] (iconfluence) -> (k-iconfluence);
    \draw[impl] (k-iconfluence) -> (1-iconfluence);
    \draw[impl] (istrengthstar) -> (ipreservation);
    \draw[impl] (0-isafety) -> (1-isafety);
    \draw[impl] (1-isafety) -> (k-isafety);
  \end{tikzpicture}

  \caption{
    An illustration of the relationship between various \iconfluence{}
    alternatives. We have proven bold implications in both directions. For
    example, we have proven both \iconfluence $\protect \centernot \implies$
    \istrengthstar.
  }
  \label{fig:iconfluence-alternatives}
\end{figure}
